% intro

\en{Mathematics}\ru{Математика}\en{, or math for short,}
\en{is abstract}\ru{абстрактна}.
\en{Abstract is the~adjective of~math}\ru{Абстрактная\:--- прилагательное математики},
\en{math is the~noun of~abstract}\ru{математика\:--- существительное абстрактной}.
\inquotesx{\hspace{-0.3ex}\en{Abstract}\ru{Абстрактное}}[,]
\inquotes{\en{theoretical}\ru{теоретическое}}
\en{and }\ru{и~}\inquotes{\en{mathematical}\ru{математическое}}
\en{are}\ru{это}
\en{synonyms}\ru{синонимы}.
\en{When}\ru{Когда}
\en{someone}\ru{кто-нибудь}
\en{is doing math}\ru{занимается математикой},
\en{he’s}\ru{он}
\en{playing}\ru{играет}
\en{a~game}\ru{в~игру}
\en{in the~far-far-away}\ru{в~далёком-предалёком}
\en{magical}\ru{волшебном}
\en{world of~imagination}\ru{мире воображения}.

\en{For example}\ru{Например},
\en{numbers}\ru{ч\'{и}сла}
\en{are}\ru{это}
\en{not real entities at all}\ru{в\'{о}все не реальные сущности}.
\en{They are}\ru{Они\:---}
\en{purely}\ru{чисто}
\en{imaginary}\ru{воображаемые}
\en{concepts}\ru{понятия},
\en{nonsense}\ru{нонсенс}.
\en{We}\ru{Мы}
\en{cannot}\ru{не~можем}
\en{experience, sensate}\ru{почувствовать, ощутить}
\en{numbers}\ru{ч\'{и}сла},
\en{can’t}\ru{не~можем}
\en{touch}\ru{потрогать}
\en{or}\ru{или}
\en{smell}\ru{понюхать}
\en{them}\ru{их}.
\en{Yep}\ru{Да},
\en{one}\ru{кто\hbox{-}то}
\en{can}\ru{может}
\en{compose}\ru{сочинять}
\en{stories}\ru{истории}
\en{about them}\ru{про них},
\en{such as}\ru{такие как}
${1 \hspace{-0.2ex} + \hspace{-0.1ex} 1 \hspace{-0.2ex} = \hspace{-0.1ex} 2}$.
\en{But}\ru{Но}
\en{no one can ever}\ru{никто никогда не~сможет}
\en{feel, perceive}\ru{чувствовать, ощущать}
\en{such an~operation}\ru{такую операцию},
\en{since}\ru{поскольку}
\en{there are no such things}\ru{не~существует ничего такого}\ru{,}
\en{as}\ru{как}
\emph{\en{one}\ru{один}}
\en{and}\ru{и}~\emph{\en{two}\ru{два}}\footnote{%
\en{I’m not about}\ru{Я не про}
\emph{\en{two apples}\ru{два яблока}}
\en{or}\ru{или}
\emph{\en{two similar bananas}\ru{два похожих банана}}
\en{for}\ru{на}
\emph{\en{a~couple of~days}\ru{п\'{а}ру дней}},
\en{but about}\ru{но про}
\ru{сам\'{о} }\en{the~}\en{number}\ru{число}~\en{\inquotes{two} itself.}\ru{\inquotesx{два}[.]}%
}\hbox{\hspace{-0.5ex}.}

\en{And}\ru{И}
\inquotesx{\en{synthesized by imagination}\ru{синтезированное воображением}}[---]
\en{it’s not only}\ru{это не~только}
\en{about numbers}\ru{о~числах}.
\en{Geometric objects}\ru{Геометрические объекты},
\en{be it}\ru{будь то}
\en{a~point}\ru{точка},
\en{a~line}\ru{линия},
\en{a~triangle}\ru{трёхуг\'{о}льник}
\en{or}\ru{или}
\en{a~plane}\ru{плоскость},
\en{and all kinds of~adventures with them}\ru{и~всевозможные приключения с~ними}
\en{are mind derived as~well}\ru{тоже производятся разумом}.

\section{\en{The ancient but intuitive geometry}\ru{Древняя, но интуитивно понятная геометрия}}

\en{\dropcap{F}{or nearly}}\ru{\dropcap{Г}{де\hbox{-}то}}
\en{two thousand years}\ru{две тысячи лет}\en{,}
\en{the~freedom of human’s thought}\ru{свобода мысли человека}
\en{was limited}\ru{была ограничена}
\en{by the~fairy tale}\ru{сказочной историей}
\en{about}\ru{про}
\en{imaginary}\ru{воображаемые}
\ru{совершенно прямые}\en{perfectly straight}
\en{one-dimensional}\ru{одномерные}
\en{lines}\ru{линии}
\en{between}\ru{между}
\en{some}\ru{какими-нибудь}
\en{two}\ru{двумя}
\en{absolutely dimensionless}\ru{абсолютно безмерными}
\en{points}\ru{точками}
\en{and beyond}\ru{и~дальше},
\en{on and on to}\ru{аж до}
\en{the~very}\ru{с\'{а}мой}
\textgreek{άπειρο}~(\en{infinity}\ru{бескон\'{е}чности})
\en{down and up the~both sides}\ru{вниз и~вверх в~обе стороны},
\en{about}\ru{про}
\en{imaginary}\ru{воображаемые}
\en{and completely flat}\ru{и~всец\'{е}ло плоские}
\en{planes}\ru{плоскости}-\en{tripoints}\ru{трёхточечники},
\en{or}\ru{или}
\ru{трёхуг\'{о}льники}\en{tri\-gons~(tri\-an\-gles)}\hspace{-0.3ex}\footnote{%
\en{Notwithstanding that}\ru{Несмотря на~то, что}
\en{just}\ru{лишь}
\en{three angles}\ru{три угла}
\en{do not define}\ru{не~определяют}
\en{a~tri\-angle}\ru{тре\-уголь\-ник}
\en{uniquely}\ru{однозначно}\en{,}
\en{precise up to}\ru{с~точностью до}
\en{translating}\ru{транслирования},
\en{mirroring}\ru{зеркалирования}
\en{and }\ru{и~}\en{rotating}\ru{вращения}.%
}\hbox{\hspace{-0.5ex}},
\en{with shortest distances}\ru{с~кратчайшими расстояниями}
\en{between points}\ru{между точками}
\en{in straight lines}\ru{по прям\'{ы}м линиям},
\en{with always}\ru{со всегда}
\en{equal}\ru{равными}
\en{to each other}\ru{между собою}
\inquotes{\en{straight}\ru{прямыми}}\en{ or~\inquotes{\textcolor{gray}{\st{st}}r\textcolor{gray}{\st{a}}ight}}
\en{angles}\ru{углами},
\en{as well as}\ru{а~ещё}
\en{about}\ru{про}
\en{many other}\ru{многие другие}
\en{pretty funny}\ru{весьма забавные}
\en{mythical}\ru{мифические}
%%\en{so to~say}\ru{так сказать}
\en{characters}\ru{персонажи}
\en{and}\ru{и}
\en{piquant relations}\ru{пикантные отношения}
\en{between them}\ru{между ними}.
%
\en{Over}\ru{Б\'{о}лее}
\en{two thousand years}\ru{двух тысяч лет}
\en{people}\ru{люди}
\en{were in captivity}\ru{были в~плену},
\en{in slavery}\ru{в~рабстве}
\en{to the~idea}\ru{у~идеи}
\en{about the~existænce}\ru{о~существовании}
\en{of the~only one}\ru{только лишь одной}
\textgreek{ευκλείδειος}
\textgreek{γεωμετρίας}~(\en{the~}\textgreek{εὐκλείδ}’\en{ean}\ru{овой}
\en{geometry}\ru{геометрии}),
\en{and}\ru{а}
\en{the~magic world}\ru{волшебный мир},
\en{described by it}\ru{ею описываемый},
\en{was equated}\ru{уравнивался}
\en{in the~past}\ru{в~прошлом}
\en{with the~real space}\ru{с~реальным пространством}
\en{around themselves}\ru{вокр\'{у}г сам\'{и}х себя}.

\href{https://el.wikipedia.org/wiki/%CE%95%CF%85%CE%BA%CE%BB%CE%B5%CE%AF%CE%B4%CE%B7%CF%82}{%
\textgreek{Εὐκλείδης}
Eὐkleídēs
\en{Euclid}\ru{Эуклид},
\textgreek{ευκλείδειος}
euclidean \ru{(эуклидово)}%
}

\textgreek{ευκλείδεια γεωμετρία}

the~plane geometry, or the two\hbox{-}dimensional euclidean geometry

\textgreek{Στοιχεῖα}
Stoikheîa
Elements, Principles

\vspace{.5em}

\subsection{Points}

{\small
\setlength{\parindent}{0pt}

\nopagebreak%
\begin{multicols}{2}
%
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Στοιχεῖα Εὐκλείδου}}}\\
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Βιβλίον I}}}\\[.3em]
\textgreek{Ορος}~\textgreek{α΄}\:(1)\\[.1em]
\textgreek{Σημεῖόν ἐστιν, οὗ μέρος οὐθέν.}

\columnbreak
%
\makebox[\columnwidth]{Euclid’s Elements}\\
\makebox[\columnwidth]{Book I}\\[.3em]
Term~\textgreek{α΄}\:(1)\\[.1em]
A point is that which has no part.
%
\end{multicols}
\par}

This description
shows that
Euclid imagines a~point
as
an indivisible location,
without width,
length
or
breadth.

\subsection{Lines, curved and straight}

{\small
\setlength{\parindent}{0pt}

\nopagebreak%
\begin{multicols}{2}
%
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Στοιχεῖα Εὐκλείδου}}}\\
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Βιβλίον I}}}\\[.3em]
\textgreek{Ορος}~\textgreek{β΄}\:(2)\\[.1em]
\textgreek{Γραμμὴ δὲ μῆκος ἀπλατές.}

\columnbreak
%
\makebox[\columnwidth]{Euclid’s Elements}\\
\makebox[\columnwidth]{Book I}\\[.3em]
Term~\textgreek{β΄}\:(2)\\[.1em]
A line is breadthless length.
%
\end{multicols}
\par}

\inquotes{Line} is the second primitive term in the Elements.
\inquotes{Breadthless length}
says that a~line will have one dimension, length, but it won’t have breadth.
The terms \inquotes{length} and \inquotes{breadth} are not defined in the Elements.

Linear lines

\subsection{A~relation between lines and points}

{\small
\setlength{\parindent}{0pt}

\nopagebreak%
\begin{multicols}{2}
%
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Στοιχεῖα Εὐκλείδου}}}\\
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Βιβλίον I}}}\\[.3em]
\textgreek{Ορος}~\textgreek{γ΄}\:(3)\\[.1em]
\textgreek{Γραμμῆς δὲ πέρατα σημεῖα.}

\columnbreak
%
\makebox[\columnwidth]{Euclid’s Elements}\\
\makebox[\columnwidth]{Book I}\\[.3em]
Term~\textgreek{γ΄}\:(3)\\[.1em]
The ends of a~line are points.
%
\end{multicols}
\par}

This statement doesn’t mention how many ends a~line can have.

\subsection{Do straight lines exists?}

\en{The~hypothesis}\ru{Гипотеза}
\en{on the existænce}\ru{о~существовании}
\en{of straight lines}\ru{прямых линий}.

\noindent
The existænce of
Euclidean straight lines
in space.

{\small
\setlength{\parindent}{0pt}

\nopagebreak%
\begin{multicols}{2}
%
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Στοιχεῖα Εὐκλείδου}}}\\
\makebox[\columnwidth]{\href{http://www.physics.ntua.gr/~mourmouras/euclid/book1/elements1.html}{\textgreek{Βιβλίον I}}}\\[.3em]
\textgreek{Ορος}~\textgreek{δ΄}\:(4)\\[.1em]
\textgreek{Εὐθεῖα γραμμή ἐστιν, ἥτις ἐξ ἴσου τοῖς ἐφ' ἑαυτῆς σημείοις κεῖται.}

\columnbreak
%
\makebox[\columnwidth]{Euclid’s Elements}\\
\makebox[\columnwidth]{Book I}\\[.3em]
Term~\textgreek{δ΄}\:(4)\\[.1em]
A~straight line is a~line which lies evenly with the~points on itself.
%
\end{multicols}
\par}

\en{To~draw a~straight line}\ru{Начертить прямую линию}
\en{by hand}\ru{рукой}
\en{is absolutely impossible}\ru{абсолютно невозможно}.

\subsection{Vectors. Lines and vectors}

\subsection{The existænce of vectors. Do vectors exist?}

\subsection{Continuity of line}

\subsection{A~point of reference}

\subsection{Translation as the easiest kind of motion. Translations and vectors}

\subsection{Straight line and vector}

\en{A~(geometric) vector}\ru{Вектор~(геометрический)} \en{may be}\ru{может быть} \en{like}\ru{как} \en{a~straight line}\ru{прямая линия} \en{with an~arrow}\ru{со стрелкой} \en{at one of its ends}\ru{на одном из её концов}.
\textcolor{red}{Then} it is fully described (characterized) by the~magnitude and the~direction.

\en{Within}\ru{в}~\href{https://en.wikipedia.org/wiki/Abstract_algebra}{\en{the abstract algebra}\ru{абстрактной алгебре}}\en{,} \en{the word}\ru{слово} \emph{\en{vector}\ru{вектор}}\en{ is}\ru{\:---} \en{about any object}\ru{про любой объект}\ru{,} \en{which}\ru{который} \en{can be}\ru{может быть} \en{summed}\ru{суммирован} \en{with similar objects}\ru{с~подобными объектами} \en{and}\ru{и}~\en{scaled~(multiplied)}\ru{умножен~(scaled)} \en{by scalars}\ru{на скаляры}, \en{and }\ru{а~}\en{vector space}\ru{векторное пространство}\en{ is}\ru{\:---} \en{a~synonym}\ru{синоним} \en{of~}\en{linear space}\ru{линейного пространства}.
\en{Therefore}\ru{Поэтому} \en{I clarify that}\ru{я поясняю, что} \en{in this book}\ru{в~этой книге} \emph{\en{vector}\ru{вектор}} \en{is}\ru{есть} \en{nothing else than}\ru{не что иное, как} \en{three-dimensional}\ru{трёхмерный} \en{geometric}\ru{геометрический} (\textgreek{Ευκλείδειος}, \ru{Евклидов, }Euclidean) \en{vector}\ru{вектор}.

\textcolor{magenta}{Why are vectors always straight (linear)?}

(a) \textcolor{magenta}{Vectors are linear (straight), they cannot be curved.}

(b) \textcolor{magenta}{Vectors are neither straight nor curved.}
A~vector has the~magnitude and the~direction.
A~vector is not a~line or a~curve, albeit it can be represented by a~straight line.

\textcolor{red}{Vector can’t be thought of as a~line.}

\subsection{\en{The line which figures real numbers}\ru{Линия, изображающая реальные числа}}

often just
\inquotes{\en{number line}\ru{числовая прямая}}

\subsection{What is a distance?}

\subsection{\en{Plane and more dimensional space}\ru{Плоскость и более многомерное пространство}}

\subsection{\en{Distance on plane or more dimensional space}\ru{Расстояние на плоскости или в более-мерном пространстве}}

\subsection{What is an angle?}

angle~$\equiv$~\textcolor{magenta}{inclination /slope, slant/ of two lines}

two lines sharing a~common point are usually called intersecting lines

angle~$\equiv$~\textcolor{magenta}{the amount of rotation of line or plane within space}

angle~$\equiv$~\textcolor{blue}{the result of the dot product of two unit vectors gives angle’s cosine}

\subsection{\en{Differentiation of continuous into small differential chunks}\ru{Дифференциация непрерывного на м\'{а}лые дифференциальные кусочки}}

\en{small differential chunks}\ru{м\'{а}лые дифференциальные кусочки}

infinitesimal (infinitely small)

\begin{changemargin}{\parindent}{\parindent}
%%\vspace{-2.5em}
{\noindent\small
\setlength{\parskip}{\spacebetweenparagraphs}

\en{A~mention}\ru{Упоминание}
\en{of~tensors}\ru{тензоров}
\en{may scare away the~reader}\ru{может отпугнуть читателя},
\en{commonly avoiding needless complications}\ru{обычно избегающего ненужных сложностей}.
\en{Don’t be afraid}\ru{Не бойся}:
\en{tensors}\ru{тензоры}
\en{are used}\ru{используются}
\en{just}\ru{просто}
\en{due to their wonderful property}\ru{из\hbox{-}за своего чудесного свойства}
\en{of the invariance}\ru{инвариантности}\:---
\en{the independence}\ru{независимости}
\en{from a~coordinate system}\ru{от системы координат}.
%
\par}
\vspace{-1.4em}
\end{changemargin}
